GO and KEGG Term Enrichment

### 2025-02-04 G85R GOandKEGGTermEnrichment.Rmd
small patches

source('/Users/johncsantiago/Documents/GitHub/WhartonLab/G85R.GOandKEGGPlottingFunctions.R')

@@

##which ranks of categories to use
##a vector of numbers specifying which ranks to use
##eg. c(1, 5:6) will use the first, fifth and sixth most sig. cats.
##can also just type 'sigs' 
usecats=c(1:20)
#usecats = 'sigs'

@@

##can be the exact name or 5 digit code in quotes
specific.kegg = "00980"

@@

##5 digits from KEGG ID
PathwayID = "00010"

@@

##can be the exact name or 5 digit code in quotes
specific.kegg = "00010"

@@

##the 7 digits of a GOterm id or the exact term name
specific.go = '0005811'

@@

@@

G85R.plotparentcat.genes(parent.category, plot.data)

@@

##a parent category generated in the treemapPlot function
##parent.category = 'small molecule biosynthetic process'

G85R.compareparent.genes(parent.category, plot.data)
##dot size is relative to the max FDR of either condition

>>>>

```{r echo = F, message = F, warning = F}

source('https://raw.githubusercontent.com/johncsantiago/WhartonLab/refs/heads/master/G85R.GOandKEGGPlottingFunctions.R')

@@

##plots the specified most significantly enriched KEGG categories
##which ranks of categories to use
##usecats is a vector of numbers specifying which ranks to use
##eg. c(1, 5:6) will use the first, fifth and sixth most sig. cats.
##can also just type 'sigs' 
usecats=c(1:20)
#usecats = 'sigs'

@@

##can be the exact name or 5 digit code in quotes
specific.kegg = "00230"

@@

##Color is relative to Fold Change

##5 digits from KEGG ID
PathwayID = "00230"

@@

##Uses data from both comparisons
##Plot all of the genes in the selected KEGG category
##Size is relative to significance

##can be the exact name or 5 digit code in quotes
specific.kegg = "00230"

@@

##the 7 digits of a GOterm id or the exact term name
specific.go = '0022008'

@@

##This function is very slow
## BP, CC, or MF
GO.ontology = 'BP'

@@

G85R.plotparentcat.genes(parent.category, plot.data, sigs.only = T)

@@

##a parent category generated in the treemapPlot function
##parent.category = 'neurogenesis'

G85R.compareparent.genes(parent.category, plot.data, sigs.only = T)
##dot size is relative to the max FDR of either condition
